[dcpo_demsupport]

### 2020-06-25 paper/dcpo_demsupport.Rmd
extract x_pred from claassen_m5 and save for (a) comparison table 👀@Tyhcass and (b) analysis replication 👀@sammo3182

```{r claassen_input}
supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc")

@@

```{r claassen_m5, eval=FALSE}
claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
                           data = claassen_input,
                           iter = 2000,
                           warmup = 1000,
                           chains = 4,
                           cores = 4,
                           thin = 2,
                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))

save(claassen_m5, file = "data/claassen_m5.RData")
```

```{r replication-model5, eval = FALSE}
# Before running the following lines, one should set their personal token and server in their system environment first: 
# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")

supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
  read_csv(col_types = cols(.default = col_double(), 
                            Country = col_character(),
                            CAbb = col_character(),
                            Project = col_character()))

# Required by the replication file
library(MASS)
library(arm)
library(dplyr)
library(tidyr)
library(rstan)
library(loo)
library(ggplot2)
library(RColorBrewer)

# options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

# working directory
WD = getwd()
setwd(WD)

# read support for dem data
sddem1 = read.csv("supdem raw survey marginals.csv")

# remove NAs
sddem1 = sddem1[!sddem1$Response==0, ]

# create year by country indicators
year0 = 1987
sddem1 = sddem1[sddem1$Year > year0,]
sddem1 = unite(sddem1, YearCountry, c(Year, Country), sep = "_", remove = FALSE)

# create item by country indicators
sddem1 = unite(sddem1, ItemCnt, c(Item, Country), sep = "_", remove = FALSE)

# create year by project indicators
sddem1 = unite(sddem1, YrProj, c(Year, Project), sep = "_", remove = FALSE)

# create year by project by country indicators
sddem1 = unite(sddem1, YrProjCnt, c(YrProj, Country), sep = "_", remove = FALSE)

# factorise
sddem1$Country = as.factor(as.character(sddem1$Country))
sddem1$Item = as.factor(as.character(sddem1$Item))
sddem1$ItemCnt = as.factor(as.character(sddem1$ItemCnt))
sddem1$Project = as.factor(as.character(sddem1$Project))
sddem1$YrProj = as.factor(as.character(sddem1$YrProj))
sddem1$YrProjCnt = as.factor(as.character(sddem1$YrProjCnt))
sddem1$Year = sddem1$Year-year0

# count data
dim(sddem1)[1]                   # 3765 national responses
length(unique(sddem1$Country))   # 150 countries
length(unique(sddem1$Project))   # 14 projects
length(unique(sddem1$Item))      # 52 items
length(unique(sddem1$ItemCnt))   # 1453 item-country
length(unique(sddem1$YrProjCnt)) # 1390 national surveys
length(unique(sddem1$Year))      # 27 unique years (out of 30)
sum(sddem1$Sample) / dim(sddem1)[1] * length(unique(sddem1$YrProjCnt))   # 1,804,450 respondents

# drop countries with less than 2 years of data
cnt.obs.years = rowSums(table(sddem1$Country, sddem1$Year) > 0)
sort(cnt.obs.years)
sddem2 = sddem1[sddem1$Country %in% levels(sddem1$Country)[cnt.obs.years > 1], ]
length(unique(sddem2$Country))   # 137 countries with 2+ years of data

#### Stan estimation

# prepare data for stan
n.items = length(unique(sddem2$Item))
n.cntrys = length(unique(sddem2$Country))
n.yrs = 2017-year0
n.proj = length(unique(sddem2$Project))
n.resp = dim(sddem2)[1]
n.itm.cnt = length(unique(sddem2$ItemCnt))
n.cntry.yrs = n.cntrys * n.yrs
n.yr.proj.cnt = length(unique(sddem2$YrProjCnt))
cntrys = as.numeric(factor(sddem2$Country))
cnt.names = as.character(sort(unique(sddem2$Country)))
cnt.code = as.character(sddem2[match(cnt.names, sddem2$Country), "CAbb"])
cnt.code[83] = "MNE"
cnt.code[106] = "SRB"
items = as.numeric(factor(sddem2$Item))
yrs = sddem2$Year
projs = as.numeric(factor(sddem2$Project))
itm.cnts = as.numeric(factor(sddem2$ItemCnt))

# specify data for stan
dat.1 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, jj=cntrys, tt=yrs, kk=items, 
             x=sddem2$Response, samp=sddem2$Sample)
dat.2 = list(N=n.resp, K=n.items, T=n.yrs, J=n.cntrys, P=n.itm.cnt, jj=cntrys, tt=yrs, 
             pp=itm.cnts, kk=items, x=sddem2$Response, samp=sddem2$Sample)
sapply(dat.2, summary)

# pars
pars.4 = c("mu_lambda","sigma_lambda","sigma_theta","phi","lambda","theta","x_pred","log_lik")
pars.5 = c("mu_lambda","sigma_lambda","sigma_delta","sigma_theta","phi","lambda","delta","theta",
            "x_pred","log_lik")
pars.6 = c("Sigma","Omega","sigma_delta","sigma_theta","phi","lambda","gamm","delta","theta",
           "x_pred","log_lik")

# iterations
n.iter = 500
n.warm = 250
n.chn = 4
n.thin = 1

# best model from PA article (model 5)
stan.mod.5 = stan(file='supdem.stan.mod5.stan', data=dat.2, pars=pars.5, 
                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
                   control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))

# model 5 with different priors
stan.mod.5.2 = stan(file='supdem.stan.mod5.2.stan', data=dat.2, pars=pars.5, 
                  iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
                  control=list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))

# model 5 with item slopes
stan.mod.6 = stan(file='supdem.stan.mod6.2.stan', data=dat.2, pars=pars.6, 
                   iter=n.iter, warmup=n.warm, chains=n.chn, thin=n.thin, 
                   control=list(adapt_delta=0.99, stepsize=0.01, max_treedepth=13))
```

>>>>

```{r claassen_input}
# Note that before running `dataverse::get_file()` below, one should set their personal token and server in their system environment first: 
# Sys.setenv("DATAVERSE_KEY" = "exampleToken")
# Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
# These values can be set to persist across R sessions using `usethis::edit_r_environ()`

supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc")

@@

```{r claassen_m5, eval=FALSE}
claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
                           data = claassen_input,
                           iter = 2000,
                           chains = 4,
                           cores = 4,
                           thin = 2,
                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))

save(claassen_m5, file = "data/claassen_m5.rda")

claassen_m5_x_pred <- rstan::extract(claassen_m5, pars = "x_pred")

save(claassen_input, claassen_m5_x_pred, file = "data/claassen_m5_x_pred.rda")
```

```{r comparison_table}

```
